\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=2cm]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{fancyhdr}

% ── Colours ──────────────────────────────────────────────────
\definecolor{oxford}{HTML}{002147}
\definecolor{accent}{HTML}{E67E22}
\definecolor{muted}{HTML}{7F8C8D}

% ── Layout ───────────────────────────────────────────────────
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\small\textcolor{muted}{Bruno Chikeka $\mid$ Sa\"{i}d Business School, University of Oxford $\mid$ \today}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0.4pt}
\setlength{\headheight}{14pt}

\hypersetup{
  colorlinks=true,
  linkcolor=oxford,
  urlcolor=oxford,
}

\begin{document}

% ── Header ───────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries\color{oxford} Seeking Co-Creators}\\[0.4em]
  {\Large Programme Structural Intelligence Engine (PSIE)}\\[0.3em]
  {\normalsize\textcolor{muted}{A research tool that makes the invisible topology of major programmes visible, analysable, and actionable.}}
\end{center}

\vspace{0.8em}
\noindent\textcolor{oxford}{\rule{\textwidth}{0.6pt}}
\vspace{0.5em}

% ── The Pitch ────────────────────────────────────────────────
\noindent\textbf{\textcolor{accent}{The Problem.}}\quad
91.5\,\% of megaprojects overrun on budget or schedule (Flyvbjerg, 16,000+ projects). The root cause: leaders cannot see the \emph{topology of interdependencies}---the hidden web through which a delay in one workstream cascades into failures elsewhere. Gantt charts show sequence; risk registers list items. Neither reveals \emph{structure}.

\noindent\textbf{\textcolor{accent}{The Tool.}}\quad
PSIE encodes a major programme as a \textbf{typed knowledge graph}, then applies network analysis, cascade simulation, and (in later phases) Bayesian prediction to reveal structural vulnerabilities invisible to conventional controls. Think of it as a \emph{structural MRI} for programmes.

\noindent\textbf{\textcolor{accent}{What Exists Today.}}\quad
A working MVP: 23-node Oman Vision 2040 case study, three S\textsuperscript{3} analytical lenses, cascade simulator, interactive dashboard. Open-source on GitHub.

% ── Architecture ─────────────────────────────────────────────
\vspace{0.5em}
\begin{table}[h!]
\centering
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{\textwidth}{@{}c l l c X@{}}
\toprule
\textbf{Layer} & \textbf{Component} & \textbf{Tradition} & \textbf{Status} & \textbf{Expertise Needed} \\
\midrule
6 & Interpretation & S\textsuperscript{3} Framework & Design & Programme management \\
5 & Calibration & Reference Class Forecasting & Planned & Empirical data access \\
4 & Prediction & Bayesian Networks & Planned & Probabilistic graphical models \\
3 & Temporal Model & System Dynamics & Stub & ODE modelling, feedback systems \\
\rowcolor{green!8}
2 & Propagation & Network Science & \textbf{Built} & Graph theory, percolation \\
\rowcolor{green!8}
1 & Graph Schema & DSMs / Syst.\ Eng.\ & \textbf{Built} & Knowledge-graph design \\
\bottomrule
\end{tabularx}
\end{table}

% ── What I'm Looking For ─────────────────────────────────────
\vspace{0.3em}
\noindent\textbf{\textcolor{oxford}{\large What I'm Looking For}}
\vspace{0.3em}

\begin{table}[h!]
\centering
\small
\renewcommand{\arraystretch}{1.25}
\begin{tabularx}{\textwidth}{@{}l X l@{}}
\toprule
\textbf{Domain} & \textbf{Contribution} & \textbf{Phase} \\
\midrule
Network Science & Validate cascade model; percolation thresholds; multiplex graphs & Now--2027 \\
System Dynamics & Build ODE-based temporal layer; feedback loop modelling & 2027 \\
Bayesian Inference & Design probabilistic prediction engine; CPT estimation & 2027--2028 \\
Programme Data & Access to historical datasets (Crossrail, HS2, etc.)\ for calibration & 2027--2029 \\
NLP / AI & Automated graph extraction from Primavera P6, risk registers & 2028 \\
Software Engineering & Scalable graph computation; interactive UI & Ongoing \\
\bottomrule
\end{tabularx}
\end{table}

% ── What You Get ─────────────────────────────────────────────
\vspace{0.3em}
\noindent\textbf{\textcolor{oxford}{\large What You Get}}
\vspace{0.3em}

\begin{itemize}[leftmargin=1.5em, itemsep=2pt]
  \item \textbf{Co-authorship} on publications from your research stream.
  \item \textbf{A novel application domain} for your methods---major programmes are a rich, under-explored graph-theoretic testbed.
  \item \textbf{Access to a working prototype} you can extend with your own models.
  \item \textbf{Real-world validation data} from national-scale programmes.
\end{itemize}

% ── Contact ──────────────────────────────────────────────────
\vspace{0.8em}
\noindent\textcolor{oxford}{\rule{\textwidth}{0.6pt}}
\vspace{0.3em}

\begin{center}
  {\large\bfseries\color{oxford} Bruno Chikeka}\\[0.2em]
  MSc Major Programme Management, Sa\"{i}d Business School, University of Oxford\\
  Supervisor: Prof.\ Daniel Armanios\\[0.3em]
  \texttt{GitHub:} \url{https://github.com/chiKeka/psie}
\end{center}

\end{document}
